Supplementary Materials

### 2019-12-05 manuscript/supplementary.Rmd
getting rid of extra files

---
title: "Supplementary Materials"
author: ""
date: 
output:
  html_document: 
    keep_md: TRUE
  pdf_document:
    includes:
      in_header: format/mystyle.sty
  word_document:
    reference_docx: format/word_styles_reference_01.docx
---

@@

## S1. Estimating travel times to the nearest ARMC 
We used two raster inputs: 1) the travel time estimates generated using the friction surface from the Malaria Atlas Project (REF) at an ~1 km^2 scale and the locations of existing ARMC and 2) the population estimates which we resampled from the World Pop raster of population originally at an N resolution. We then extracted the mean of travel times weighted by the population in that grid cell for each district or commune to get administrative level estimates of travel times to the nearest ARMC. Figure S1.1 shows the raster inputs as well as the resulting estimates of travel times at the admin level.

>>>>

---
title: "Supplementary Materials"
author: ""
date: 
output:
  github_document: 
  html_document: default
  pdf_document:
    includes:
      in_header: format/mystyle.sty
  word_document:
    reference_docx: format/word_styles_reference_01.docx
---

@@

## S1. Estimating travel times to the nearest ARMC 
We used two raster inputs: 1) the travel time estimates generated using the friction surface from the Malaria Atlas Project (REF) at an ~1 km^2 scale and the locations of existing ARMC and 2) the population estimates which we resampled from the World Pop raster of population originally at an N resolution. We then extracted the mean of travel times weighted by the population in that grid cell for each district or commune to get administrative level estimates of travel times to the nearest ARMC. Figure S1 shows the raster inputs as well as the resulting estimates of travel times at the admin level.
